### 2014-11-02 thesis/results/results.tex
Add code for all trauma plots

Out of all four automatic feature selection methods, the single feature that
was deemed to be the most important in predicting LOS was \texttt{EpisodeType}.
Although this was a general hospital-wide data set, the importance of this
attribute indicates that condition-specific factors should be taken into
account when predicting the LOS for any medical domain. Additionally, the
\texttt{InpatientService} feature was also considered important in predicting
the class, a finding that was also noted by \cite{Lucas2009}, although they
considered the classification of LOS $\leq$ and > 3 days.

\section{Comparison of Classifiers}
\subsection{Trauma Data Set}

>>>>

Out of all four automatic feature selection methods, the single feature that
was deemed to be the most important in predicting LOS was \texttt{EpisodeType}.
Although this was a general hospital-wide data set, the importance of this
attribute indicates that condition-specific factors should be taken into
account when predicting the LOS for any medical domain. Additionally, the
\texttt{InpatientService} feature was also considered important in predicting
the class, a finding that was also noted by Lucas et al. \cite{Lucas2009},
although they considered the classification of LOS $\leq$ and $>$ 3 days.

\section{Comparison of Classifiers}
\begin{figure}[htbp]
\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-nofs-acc.eps}
\caption{1a}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-nofs-auc.eps}
\caption{1b}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-dinh-acc.eps}
\caption{1a}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-dinh-auc.eps}
\caption{1b}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-expert-acc.eps}
\caption{1a}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-expert-auc.eps}
\caption{1b}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-cfs-acc.eps}
\caption{1a}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-cfs-auc.eps}
\caption{1b}
\label{}
\end{subfigure}
\caption{plots of}
\label{}
\end{figure}

\begin{figure}
\ContinuedFloat

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-wrapper-acc.eps}
\caption{1a}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-wrapper-auc.eps}
\caption{1b}
\label{}
\end{subfigure}
\caption{plots of}
\label{}
\end{figure}

\begin{figure}[htbp]
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-corr.eps}
\caption{}
\label{}
\end{subfigure}
\caption{}
\label{}
\end{figure}

\begin{figure}[htbp]
\ContinuedFloat
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-ig.eps}
\caption{}
\label{}
\end{subfigure}
\end{figure}

\begin{figure}[htbp]
\ContinuedFloat
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-oner.eps}
\caption{}
\label{}
\end{subfigure}
\end{figure}

\subsection{Trauma Data Set}
